 \documentclass[a4paper,12pt]{article}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{eurosym}
\usepackage{vmargin}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{framed}
\usepackage{subfigure}
\usepackage{fancyhdr}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2570}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{LastRevised=Wednesday, February 23, 2011 13:24:34}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{Language=American English}

%\pagestyle{fancy}
\setmarginsrb{20mm}{0mm}{20mm}{25mm}{12mm}{11mm}{0mm}{11mm}
%\lhead{MA4413 2013} \rhead{Mr. Kevin O'Brien}
%\chead{Midterm Assessment 1 }
%\input{tcilatex}

\begin{document}
\Large
%\subsection{Probability Question}

An auto insurance company has 10,000 policyholders. Each policyholder is classified as
\begin{itemize}
\item 
\item[(i)] young or old;  \textbf{\textit{(Y and O)}}
\item[(ii)] male or female; and  \textbf{\textit{(B and G)}}
\item[(iii)] married or single. \textbf{\textit{(M and S)}}
\end{itemize} 

Of these policyholders, 3000 are young, 4600 are male, and 7000 are married. The 
policyholders can also be classified as 1320 young males, 3010 married males, and 1400 
young married persons. Finally, 600 of the policyholders are young married males. 
How many of the company’s policyholders are young, female, and single? 

%\begin{itemize}
%\item[(A)] 280 
%\item[(B)] 423 
%\item[(C)] 486 
%\item[(D)] 880 
%\item[(E)] 896 
%\end{itemize}
\newpage
(blank)
\newpage
%\subsection*{Question 1}
You must create a password of length 5 using the following characters:
$\{a,b,c,d,1,2,3,4\}$.\\[-0.2cm]
\begin{enumerate}[(a)]
\item How many possible passwords are there? \item What if you only use letters? \item What if first character cannot be a number? \item How many passwords contain 
\emph{at least one} number? \item What if each character must be different?
\end{enumerate}
\newpage
(blank)
\newpage
%\subsection*{Question 2}
In your favourite RPG game, let's assume that in selecting your character there are 5 character classes and 2 genders. Let's also assume there are 3 levels of difficulty for this game.\\[-0.2cm]
\begin{enumerate}[(a)]
\item How many possible ways can you play this game? \item What if you always choose the ``warrior'' class? \item What if you always choose a female character? \item What if you always play on the highest difficulty setting? \item Let's assume the game has a two-player mode. How many possible ways can you play this game? (hint: you cannot play the game on different difficulty levels). \item What if your friend chooses a different character class to you?
\end{enumerate}
\newpage
(blank)
\newpage
%\subsection*{Question 3}
Assume that you are going to an exam and you can only bring 3 items. You have the following items:\\ $\{\text{mobile phone, } \text{pen, } \text{ruler, } \text{calculator, } \text{laptop, } \text{apple} \}$.\\[-0.2cm]
\begin{enumerate}[(a)]
\item In order to make your decision, you first \emph{arrange} these 6 items on your desk. How many possible arrangements are there? \item How many possible groups of three items can you bring with you? \item What if you decide that the pen is essential? \item What if the pen is essential and you also decide that you won't bring an apple or a laptop?
\end{enumerate}
\newpage
(blank)
\newpage
%\subsection*{Question 4}
A team of 5 people is required to perform a particular task. We are selecting from a group of 7 women and 3 men.\\[0.2cm]
How many selections are there:\\[-0.2cm]
\begin{enumerate}[(a)]
\item Altogether? \item If one of the women is an expert and must be on the team? \item If two of the individuals do not get along and cannot be on the team together? 
\item If the group must contain 3 women and 2 men? \item If the group must contain more women than men? \quad \item If the group must contain more men than women?
\end{enumerate}


\end{document}
