\documentclass[12pt]{article}

\usepackage{framed}
\usepackage{graphics}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{graphicx}
%---------------------------------------%
%opening
\title{MA4413 and MA4704}
\author{Counting, Combinations and Permutations}

\begin{document}
\section{Choose Operator}
%----------------------------------------------------------%
\begin{itemize}
%----------------------------------------------------------%


\item[1] Choose Operator
\[ {n \choose k} = \frac{n!}{k! \times (n-k)!} \]
Evaluate the following:
\begin{multicols}{3}
    \begin{enumerate}
    \item[1] ${5 \choose 2}$
    \item[2] ${5 \choose 0}$
    \item[3] ${6 \choose 3}$
    \item[4] ${6 \choose 6}$
    \item[5] ${10 \choose 1}$
    \item[6] ${10 \choose 9}$
    \end{enumerate}        
  \end{multicols}
%----------------------------------------------------------%
%Page 29
\item[2] In how many ways can a group of four people be selected from three men and four women?
In how many of these groups are there more women than men?
%----------------------------------------------------------%
%PAGE 66
\item[3] In how many ways can a group of five be selected from ten people
How many groups can be selected if two particular people from the ten can not be selected in the same group?\\
\\
\textbf{Counting Sets using Venn Diagrams}
\item[4] 
%http://www.mathsireland.com/LCHGeneralNotes/PermCombProb/5_5_Prob_MultAnd/Q_5_5_Prob_MultAnd.html
The Venn Diagram shows the number of elements in each subset of set $S$.
If $P(A) = 3/10$ and $P(B) = 1/2$, find the values of $x$ and $y$

%Page 27
\item[5] How many different four digit numners greater than 5000 can be formed from the digits \textbf{2,4,5,8,9} if each digit can only be used once in any given number. How many of these numbers are odd?
\end{itemize}


\subsection*{Question 9} %READY
%2002 Question 7

\begin{itemize}
\item[(a)] The code to open a combination lock is an ordered sequence of four digits
chosen from the set $\{1, 2, 3, 4, 5, 6, 7\}$. How many different codes are possible
\begin{itemize}
\item[(i)] if repetition is allowed?
\item[(ii)]  if repetition is not allowed? [2 Marks]
\end{itemize}
\item[(b)] Twelve balls numbered $\{1,2,3, \ldots ,12\}$ are placed in a container and three balls
are drawn at random without replacement. How many different selections of
three balls are possible, if the order of selection is not important? [2 Marks]
\item[(c)] In the experiment described in part (b), let $A$ be the event that the number on
each ball drawn is at most 5. Let $B$ be the event that the number on each ball
drawn is odd. Calculate the probability of each of the events $A$ , $B$, $A \cup B$ and $A \cap B$. [6 Marks]
\end{itemize}


\end{document}
